%!TEX program = xelatex
% Encoding: UTF8
% SEIKA 2015

%\documentclass[a4paper,11pt,twoside]{book}
\documentclass[a4paper,11pt,twoside]{ctexbook}

\usepackage{geometry}
\geometry{left=3.5cm, right=3cm, top=3cm, bottom=3cm}
%控制页眉页脚页码
\pagestyle{headings}
%罗马字符页码
%\pagenumbering{roman}

%\usepackage{ctex}    uncomment this if article is applied on docclass
%\usepackage{xeCJK}   uncomment this if article is applied on docclass

%\CJKsetecglue{} % 禁用汉字与其他内容之间空格（空隙）
%\usepackage{ctex}

% 支持西文字体
\usepackage{fourier}
\usepackage{courier}
% \usepackage{fontspec}
\newfontfamily\CodeFont{Ubuntu Mono}

\usepackage{graphicx}
% 支持插入eps图形文件
% \usepackage{epsfig}

% 支持超链接
\usepackage[colorlinks]{hyperref}

% 支持代码框插入
\usepackage{xcolor}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\definecolor{myback}{rgb}{0.95,0.95,0.95}

\usepackage{listings}
\lstset{ %
  backgroundcolor=\color{myback},    % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\linespread{0.99}\small  \CodeFont,   % the size of the fonts that are used for the code
  breakatwhitespace=false,           % sets if automatic breaks should only happen at whitespace
  breaklines=true,                   % sets automatic line breaking
  captionpos=bl,                     % sets the caption-position to bottom
  commentstyle=\color{mygreen},      % comment style
  deletekeywords={...},              % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},            % if you want to add LaTeX within your code
  extendedchars=true,                % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                      % adds a frame around the code
  keepspaces=true,                   % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},         % keyword style
  language=Python,                   % the language of the code
  morekeywords={*,...},              % if you want to add more keywords to the set
  numbers=left,                      % where to put the line-numbers; possible values are (none, left, right)
  numbersep=4pt,                     % how far the line-numbers are from the code
  numberstyle=\tiny\CodeFont\color{mygray},   % the style that is used for the line-numbers
  rulecolor=\color{mygray},          % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                  % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=true,             % underline spaces within strings only
  showtabs=true,                     % show tabs within strings adding particular underscores
  stepnumber=1,                      % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{orange},        % string literal style
  tabsize=2,                         % sets default tabsize to 2 spaces
  %title=myPython.py                 % show the filename of files included with \lstinputlisting; also try caption instead of title
}

% \setCJKmainfont[BoldFont={SimSun},ItalicFont={KaiTi}] %{SimSun}

%%%%%%%%%%%%
\title{Tensorflow 指南}
\author{}
\date{2015-12-16}
% \thanks{}

\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage

\chapter{起步}
% \section{Introduction}
\include{get_started/sec_1_1_introduction}
\section{Download and Setup}

\newpage

\section{Basic Usage}

To use TensorFlow you need to understand how TensorFlow:

\begin{itemize}
\item Represents computations as graphs.
\item Executes graphs in the context of Sessions.
\item Represents data as tensors.
\item Maintains state with Variables.
\item Uses feeds and fetches to get data into and out of arbitrary operations.
\end{itemize}

\subsection{Overview}

TensorFlow is a programming system in which you represent computations as graphs. Nodes in the graph are called ops (short for operations). An op takes zero or more \lstinline{Tensors}, performs some computation, and produces zero or more \lstinline{Tensors}. A Tensor is a typed multi-dimensional array. For example, you can represent a mini-batch of images as a 4-D array of floating point numbers with dimensions \lstinline{[batch, height, width, channels]}.

\subsection{The computation graph}

TensorFlow programs are usually structured into a construction phase, that assembles a graph, and an execution phase that uses a session to execute ops in the graph.

For example, it is common to create a graph to represent and train a neural network in the construction phase, and then repeatedly execute a set of training ops in the graph in the execution phase.

TensorFlow can be used from C, C++, and Python programs. It is presently much easier to use the Python library to assemble graphs, as it provides a large set of helper functions not available in the C and C++ libraries.

The session libraries have equivalent functionalities for the three languages.

\subsubsection {Building the graph}
To build a graph start with ops that do not need any input (source ops), such as Constant, and pass their output to other ops that do computation.

The ops constructors in the Python library return objects that stand for the output of the constructed ops. You can pass these to other ops constructors to use as inputs.

The TensorFlow Python library has a default graph to which ops constructors add nodes. The default graph is sufficient for many applications. See the Graph class documentation for how to explicitly manage multiple graphs.

\begin{lstlisting}
import tensorflow as tf

# Create a Constant op that produces a 1x2 matrix.  The op is
# added as a node to the default graph.
#
# The value returned by the constructor represents the output
# of the Constant op.
matrix1 = tf.constant([[3., 3.]])

# Create another Constant that produces a 2x1 matrix.
matrix2 = tf.constant([[2.],[2.]])

# Create a Matmul op that takes 'matrix1' and 'matrix2' as inputs.
# The returned value, 'product', represents the result of the matrix
# multiplication.
product = tf.matmul(matrix1, matrix2)
\end{lstlisting}

The default graph now has three nodes: two constant() ops and one matmul() op. To actually multiply the matrices, and get the result of the multiplication, you must launch the graph in a session.

\subsubsection {Launching the graph in a session}

Launching follows construction. To launch a graph, create a Session object. Without arguments the session constructor launches the default graph.

See the Session class for the complete session API.

\begin{lstlisting}
# Launch the default graph.
sess = tf.Session()

# To run the matmul op we call the session 'run()' method, passing 'product'
# which represents the output of the matmul op.  This indicates to the call
# that we want to get the output of the matmul op back.
#
# All inputs needed by the op are run automatically by the session.  They
# typically are run in parallel.
#
# The call 'run(product)' thus causes the execution of threes ops in the
# graph: the two constants and matmul.
#
# The output of the op is returned in 'result' as a numpy `ndarray` object.
result = sess.run(product)
print(result)
# ==> [[ 12.]]

# Close the Session when we're done.
sess.close()
\end{lstlisting}

Sessions should be closed to release resources. You can also enter a Session with a "with" block. The Session closes automatically at the end of the with block.

\begin{lstlisting}
with tf.Session() as sess:
  result = sess.run([product])
  print(result)
\end{lstlisting}

The TensorFlow implementation translates the graph definition into executable operations distributed across available compute resources, such as the CPU or one of your computer's GPU cards. In general you do not have to specify CPUs or GPUs explicitly. TensorFlow uses your first GPU, if you have one, for as many operations as possible.

If you have more than one GPU available on your machine, to use a GPU beyond the first you must assign ops to it explicitly. Use with...Device statements to specify which CPU or GPU to use for operations:

\begin{lstlisting}
with tf.Session() as sess:
  with tf.device("/gpu:1"):
    matrix1 = tf.constant([[3., 3.]])
    matrix2 = tf.constant([[2.],[2.]])
    product = tf.matmul(matrix1, matrix2)
    ...
\end{lstlisting}

Devices are specified with strings. The currently supported devices are:

"/cpu:0": The CPU of your machine.
"/gpu:0": The GPU of your machine, if you have one.
"/gpu:1": The second GPU of your machine, etc.
See Using GPUs for more information about GPUs and TensorFlow.

\subsection{Interactive Usage}

\subsection{Tensors}
\subsection{Variables}
\subsection{Fetches}
\subsection{Feeds}

\begin{lstlisting}
\end{lstlisting}

\begin{lstlisting}
\end{lstlisting}

\begin{lstlisting}
\end{lstlisting}

\begin{lstlisting}
\end{lstlisting}



\newpage

%\chapter{基础教程}
\include{tutorials/sec_2_1_overview}
\include{tutorials/sec_2_2_minist_beginners}
\include{tutorials/sec_2_3_minist_pros}
\include{tutorials/sec_2_4_}
\include{tutorials/sec_2_5_}

% \newpage
% \section {TensorFlow运作方式}
% \section {卷积神经网络}
% \subsection {概述}
% \subsection {代码组织}
% \subsection {CIFAR-10模型}_
% \subsection {开始执行并训练模型}
% \subsection {模型评估}
% \section {Vector Representations of Words}
% \section {循环神经网络}
% \section {曼德博(Mandelbrot)集合}
% \section {偏微分方程}
% \section {MNIST数据集下载}


\newpage
% Chapter 3 How to...
% 第三章 运作方式
\include{how_tos/sec_3_1_variables}
% \input{how_tos/sec_1_variables}


\newpage
\chapter{资源}

\newpage
\chapter{其他}

\end{document}